My english activity log

### 2019-10-02 english-activity.Rmd
jusque 29/09

From now on, you will use this article to include every single activity that you do in English in a chronological order (e.g. reading a book in English, watching TV shows and series in English, going to an English Evening in Mons, travelling to an English-speaking country, playing games in English such as the pretty exciting game LyricsTraining, etc.). You can even write a few lines about what you’ve watched/read/done and recommend certain things to your friends. The sky’s the limit! We value personal initiative and we will be happy to read whatever you have to offer.

>>>>

.
